\begin{itemize}
    \item Re-architecture of Distributed Execution Engine, moving from an Active-Passive to an \textbf{Active-Active dual-writer} AP/CP tolerant hybrid with an in-built Disaster Recovery state machine.
    \item Led the development of an \textbf{MCP} based AI \textbf{agent} for taking actions from meeting transcripts. Increased accuracy with structured data using a modified \textbf{ReAct} prompting technique. 
    \item Delivered \textbf{Zero Downtime MongoDB to MySQL migration at 2000+ QPS} and the development of a highly available event messaging framework.
    \item Initiated the development of "vPlay," a cloud-based in-browser IDE aimed at reimagining the developer experience and mitigating left-shift inertia, with projected annual savings exceeding \textbf{\$1M}.
    \item Established and led a high-performing Bangalore Cloud Platform team of \textbf{18 members} (2 Managers + 16 Engineers), fostering collaboration and innovation.
    \item Oversaw a robust portfolio consisting of \textbf{18 microservices and frontends} and 5 SDKs, achieving year-over-year cost savings of approximately \textbf{\(\sim\)\$200M}.
    \item Strategically positioned VISA's Enterprise Cloud to evolve into a \textbf{SaaS offering} as part of a comprehensive 5-year growth plan.
    \item Championed the elevation of \textbf{Generative AI} capabilities and awareness, resulting in a \textbf{10\% increase in developer productivity} across the VISA Bengaluru Technology Center in Q1-Q2 FY-24.
    \item Led multiple site-level initiatives and actively mentored 3 employees across various teams and functions, enhancing the leadership quotient and overall technological competence of the Bengaluru Technology Center.
  \end{itemize}